Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-09-21 paper/tidy-missing-data-paper.Rmd
compilation adventures - removing duplicate code chunk

---
documentclass: jss
author:
  - name: Nicholas Tierney
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics
      E774, Menzies Building
      Monash University, Clayton
    email: \email{nicholas.tierney@gmail.com}
    url: http://www.njtierney.com
  - name: Dianne Cook
    affiliation: Monash University
title:
  formatted: "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
  # If you use tex in the formatted title, also supply version without
  plain:     "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
  # For running headers, if needed
  short:     "Explore missingness with \\pkg{naniar}"
abstract: >
  Despite the large body of research on missing value distributions and imputation, there is comparatively little literature with a focus on how to make it easy to handle, explore, and impute missing values in data. This paper addresses this gap. The new methodology builds upon tidy data principles, with the goal of integrating missing value handling as a key part of data analysis workflows. We define a new data structure, and a suite of new operations. Together, these provide a connected framework for handling, exploring, and imputing missing values. These methods are available in the R package \pkg{naniar}.
keywords:
  # at least one keyword must be supplied
  formatted: [statistical computing, statistical graphics, data science, data visualization, tidyverse, data pipeline, "\\proglang{R}"]
  plain:     [statistical computing, statistical graphics, data science, data visualization, tidyverse, data pipeline, "\\proglang{R}"]
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
    includes:
      in_preamble: preamble.tex
     #in_header: header.tex
    keep_tex: yes
    #citation_package: 'natbib'
bibliography: tidy-missing-data-paper.bib
cls: jss.cls
---

@@

```{r housing-miss-case-var, fig.cap = "The amount of missings in variables (A) and cases (B) for Melbourne housing data. (A) Build area and year built have more than 50\\% missing, and car, bathroom, bedroom2 and longitude and latitude have about 25\\% missings. (B) Cases are missing 5 - 50\\% of values. The majority of missingness is in selected cases and variables.", fig.height = 4, fig.width = 8, out.width = "100%"}
```

>>>>

---
documentclass: jss
author:
  - name: Nicholas Tierney
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics
      E774, Menzies Building
      Monash University, Clayton
    email: \email{nicholas.tierney@gmail.com}
    url: http://www.njtierney.com
  - name: Dianne Cook
    affiliation: Monash University
title:
  formatted: "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
  # If you use tex in the formatted title, also supply version without
  plain:     "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
  # For running headers, if needed
  short:     "Explore missingness with \\pkg{naniar}"
abstract: >
  Despite the large body of research on missing value distributions and imputation, there is comparatively little literature with a focus on how to make it easy to handle, explore, and impute missing values in data. This paper addresses this gap. The new methodology builds upon tidy data principles, with the goal of integrating missing value handling as a key part of data analysis workflows. We define a new data structure, and a suite of new operations. Together, these provide a connected framework for handling, exploring, and imputing missing values. These methods are available in the R package \pkg{naniar}.
keywords:
  # at least one keyword must be supplied
  formatted: [statistical computing, statistical graphics, data science, data visualization, tidyverse, data pipeline, "\\proglang{R}"]
  plain:     [statistical computing, statistical graphics, data science, data visualization, tidyverse, data pipeline, "\\proglang{R}"]
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
    includes:
      in_preamble: preamble.tex
     #in_header: header.tex
    keep_tex: yes
    citation_package: 'natbib'
# bibliography: tidy-missing-data-paper.bib
bibliography: "tidy-missing-data-paper-no-jss.bib"
cls: jss.cls
---

@@
